Self-test prime dimensional EPR pairs with constant alphabet

### 2019-04-07 Draft/draft.tex
Honghao: more details about the robustness of the linear system game and the ideal strategy

\begin{definition}[Linear system game]
 Let $Hx = c$ be an $m \times n$ system of linear equations over $\Z_2$,
 where $H$ is an $m$-by-$n$ matrix with entries in $\Z_2 = \{0,1\}$ and 
 $c$ is a length-$n$ vector with entries in $\Z_2$. 
 The associated linear system game involves two
 players Alice and Bob, where Alice is given an equation number $i \in \calX = [m]+1$ and replies with $a \in \calA = \Z_2^{\times n}$,
 and Bob is given a variable number $j \in \calY = [n]+1$ and replies with an assignment $b \in \calB = \Z_2$. The winning condition is 
 that Alice's assignment to the variables should satisfy equation $i$ and Alice's $j$-th assignment $a(j)$ should match $b$.
 Formally, the winning condition is 
 \begin{align*}
 	a(j) &= b && \text{(Consistency)} \\
	\sum_{k= 1}^n H(i,k) a(k) &\equiv c(i) \pmod 2. &&\text{(Constraint satisfaction)},
 \end{align*}
 for all $(i,j) \in \calX \times \calY$. 
\end{definition}
The scoring function of linear system games always maps an input-output pair to $\{0,1\}$, 
so later when we say a quantum strategy wins a linear system game perfectly, we mean that 
$V(a,b,x,y) =0$ implies that $\pr{ab}{xy} = 0$.  \carl{Make this clear in the definition itself.}
We focus on quantum strategies for the linear system game presented in terms of binary observables.
\begin{definition}[Quantum strategy of a linear system game]
\label{def:q_strat}
A quantum strategy for the linear system game $(Hx = c)$ consists of 
\begin{enumerate}
	\item a pair of finite Hilbert spaces $\calH_A$ and $\calH_B$;
	\item a collection of binary observables $B_j$, $1 \leq j \leq n$, on $\calH_B$
	such that $B_j^2 = \1$ for every $1 \leq j \leq n$;
	\item a collection of binary observables $A_{ij}$, $1\leq i \leq m$, $1\leq j\leq n$ 
	on $\calH_A$ such that 
	\begin{enumerate}
		\item $A_{ij}^2 = \1$ for every $i,j$,
		\item $\Pi_j A_{ij}^{H(i,j)} = (-\1)^{c(i)}$ for every $i$, and
		\item $A_{il}A_{ik} = A_{ik}A_{il}$ for every $i$ and $H(i,l) = H(i,k) =1$;
	\end{enumerate} 
	and
	\item a quantum state $\ket{\psi} \in \calH_A \x \calH_B$.
\end{enumerate}
\end{definition}
Note that any quantum strategy presented in terms of binary observables can be 
converted to a quantum strategy presented in terms of projective measurement, and
vice versa.  \carl{This is not entirely true.  A ``quantum strategy presented in terms of projective measurement'' allows
Alice to give answers that violate the ``Constraint satisfaction'' condition, while a ``quantum strategy presented 
in terms of binary observables'' does not.}

%It has been shown in Ref.~\cite{cleve2014} that the linear system game has a perfect strategy 
%satisfying conditions in \cref{def:q_strat} if and only if the linear system has a finite-dimensional
%operator solution in the following sense.  \carl{There's a missing reference here?}
%\begin{definition}[Operator solution of a linear system]
%\label{def:op_sol}
%	An operator solution to a linear system $Hx =c$ over $\Z_2$ is a sequence of \hf{finite-dimensional} Hermitian 
%	operators \hf{with finite entries}: $A_1, A_2, \dots A_n$ on a Hilbert space $\calH$ such that \carl{(What does the word ``bounded'' mean here?  It might
%	be best to just state the definition for finite dimensions only.)}
%	\begin{enumerate}
%		\item $A_i^2 = \1$, i.e. $A_i$ is a binary observable, for all $1 \leq i \leq n$;
%		\item If $x_l$ and $x_k$ appear in the same equation, then $A_l$ and $A_k$ commute;
%		\item for all $1 \leq i \leq m$,
%		\begin{align*}
%			\Pi_{k=1}^n A_k^{H(i,k)} = (-1)^{c(i)}\1.
%		\end{align*}
%	\end{enumerate}
%	A finite dimensional operator solution to a linear system $Hx = c$ over $\Z_2$ is an operator
%	solution in which the Hilbert space is finite-dimensional.
%\end{definition}
%Perfect quantum strategies can be extracted from operator solutions and vice versa.
%Another angle to look at the linear system game ($Hx = c$) is a finitely presented group
%over $\Z_2$, which is called the solution group.
%\begin{definition}[Solution group of a linear system game]
%	\label{def:presentation}
%	Let $Hx = c$ be an $m \times n$  linear system. The solution group of this system
%	is the group
%	\begin{align*}
%		\Gamma(H,c) := \ip{
%		x_1,\dots x_n, J: &J^2 = x_i^2 = e \text{ for all }1 \leq i \leq n, \\
%				& \Pi_{j=1}^n x_j^{H(i,j)} = J^{c(i)} \text{ for all } 1 \leq i \leq m, \text{ and } \\
%				& x_l x_k = x_k x_l \text{ if } H(i,k) = H(i,l) = 1 \text{ for some } i
%				} .
%	\end{align*}
%\end{definition}
%\carl{Don't you also need a commutativity condition for $J$ with $\{ x_i \}$?}
%For concepts about group presentations, we refer to Sec.~$2$ of Ref.~\cite{slofstra2017}.
%Combining \cref{def:op_sol} and \cref{def:presentation}, we know that an operator solution associated to $Hx =c$ is 
%a finite-dimensional representation of $\Gamma(H,c)$ that maps $J$ to $-\1$.

@@

Slofstra's seminal work~\cite{slofstra2017} draws our attention to the relation $xyx^{-1} = y^2$.  \carl{That sentence
is too vague -- either make it a rigorous statement or leave it out.}
\hf{We generalize this relation and make he solution group of $\LS$ the embedding of the 
following group}
\begin{align}
	\Pg_r= \langle u, o : uou^{-1} = o^r \rangle, \text{ for } r \in \N.
\end{align}
In other words, relations in the presentation of the solution group of $\LS$ can be combined to derive the
relation $uou^{-1} = o^r$.  
\begin{proposition}
	\label{prop:embed}
	The group $\Pg_r$ can be embedded into a linear system game $\LS_r$ over $\Z_2$,
	with the numbers of variables and equations linear in $r$, where each equation involves $3$ variables.
	\carl{You need to make this a more precise statement.  (It sounds as if you're saying 
	that the numbers of variables and equations is independent of $r$, which I'm pretty sure is not true.)}
\end{proposition}
The process of embedding $\Pg_r$ into the solution group of $\LS$ follows the recipe given in the proofs of
Proposition~$4.8$, Lemma~$4.4$ and Proposition $4.2$ of Ref.~\cite{slofstra2017}.
The order of applying the results is the reverse of the order they are presented in Ref.~\cite{slofstra2017}.
We give details of this embedding process in \cref{sec:power2} for $r = 2$, \cref{sec:power3} for $r = 3$, 
and \cref{sec:power5} for $r = 5$.

@@

Since Bob gets the same symbols $1$ and $2$ in different sub-tests, 
the observables $A_1 = B_1 = \Psi_1(x_1)$ and $A_2 = B_2 = \Psi_1(x_2)$ are extended from $B_1|_V$ and $B_2|_V$ as follows
%\begin{align}
%	B_1 = \ketbra{x_0}{x_0} + 
%	\sum_{k=1}^{(d-1)/2}\left( e^{ik\pi/2d}\ketbra{x_k}{x_{d-k}} + e^{-ik\pi/2d}\ketbra{x_{d-k}}{x_k}\right)\\
%	B_2 = \ketbra{x_0}{x_0} + 
%	\sum_{k=1}^{(d-1)/2}\left( e^{ik\pi/2d}\ketbra{x_{d-k}}{x_k} + e^{-ik\pi/2d}\ketbra{x_{k}}{x_{d-k}}\right)
%\end{align}
	A_1 = B_1 = \Psi_1(x_1) &= \sum_{k=1}^{(d-1)/2}\left( \omega_d^k\ketbra{x_k}{x_{d-k}} + \omega_d^{-k}\ketbra{x_{d-k}}{x_k}\right)\\
	A_2 = B_2 = \Psi_1(x_2) &= \sum_{k=1}^{(d-1)/2}\left(\ketbra{x_{d-k}}{x_k} + \ketbra{x_k}{x_{d-k}}\right).
It can be checked that $X = \Psi_1(x_1x_2) = \sum_{i \in \Zd} \omega_d^i \ketbra{x_i}{x_i}$ 
The relation $uxu^{-1} = x^r$ and $X$ determine that 
	U =\Psi_1(u) = \Psi_1(x_3x_4) =  \sum_{i \in \Zd} \ketbra{x_{r^{-1}i}}{x_i},
\hf{where $r^{-1}$ is the multiplicative inverse of $r$ in $\Zd$.
All the multiplications done on the label $i$ of the state $\ket{x_i}$ are within the group $\Zd$.}
The first step of the embedding procedure in the proof of \cref{prop:embed} requires
the commutativity between $U$ and $B_2$, so we prove the commutation relation first and
then give $\Psi_1(x_3)$ and $\Psi_1(x_4)$.
The commutation relation can be checked as follows,
	UB_2U\ct = \sum_{i=1}^{d-1} U\ketbra{x_i}{x_{d-i}}U\ct = \sum_{i=1}^{d-1} \ketbra{x_{r^{-1} i}}{x_{r^{-1}(d-i)}}.
Let $i_1 = i r^{-1} \in \Zd$ and $i_2  = r^{-1} (d-i) \in \Zd$, then
	r(i_1 + i_2) \equiv  i + (d-i) \equiv d \pmod{d} .
Let $i_1 + i_2= x \in \{2, 3 \dots 2d-2\}$, then
	rx \equiv d \pmod{d}
Since $d$ is an odd prime number and $r < d$, then $r$ cannot divide $d$ and the only valid value of $x$ is $d$.
Hence, conjugation by $U$ will transform $\ketbra{x_i}{x_{d-i}}$ into another term of the same form.
Now suppose for some $1 \leq i < i' \leq d-1$ and $U\ketbra{x_i}{x_{d-i}}U\ct = U\ketbra{x_{i'}}{x_{d-i'}}U\ct$,
it means that in $\Zd$, $i r^{-1} = i' r^{-1}$ and $i = i'$, which contradicts the fact that $i \neq i'$.
What we have shown so far is that conjugation by $U$ only permutes the terms of $B_2$, so
	UB_2U\ct = B_2.
%There are two cases to consider which are the index is dividable by $r$ or not.
%Note that in the following calculation, the division is not with respect to the modulo $d$.
%When the index $i \equiv 0 \pmod{r}$, $U\ketbra{x_i}{x_{d-i}}U = \ketbra{x_{i/2}}{x_{d-i/r}}$, and
%when the index $i \not\equiv 0 \pmod{r}$, $U\ketbra{x_i}{x_{d-i}}U = \ketbra{x_{(d+i)/2}}{x_{(d-i)/2}}$,
%so we can calculate that 
%\begin{align}
%	\sum_{i=1}^{d-1} U\ketbra{x_i}{x_{d-i}}U\ct 
%	=& \sum_{i=1}^{(d-1)/2}U\ketbra{x_{2i}}{x_{d-2i}}U\ct 
%	+ \sum_{i=0}^{(d-1)/2-1} U\ketbra{x_{2i+1}}{x_{d-(2i+1)}}U\ct\\
%	=& \sum_{i=1}^{(d-1)/2}\ketbra{x_i}{x_{d-i}} + \sum_{i=0}^{(d-1)/2-1} \ketbra{x_{(d+1)/2+i}}{x_{(d-1)/2-i}}\\
%	=& \sum_{i=1}^{(d-1)/2}\ketbra{x_i}{x_{d-i}} + \sum_{i=(d+1)/2}^{d-1} \ketbra{x_i}{x_{d-i}}\\
%	=&\sum_{i=1}^{d-1} \ketbra{x_i}{x_{d-i}}.
%\end{align}
The decomposition of $U$ into $\Psi_1(x_3)$ and $\Psi_1(x_4)$ is similar to the decomposition of $X$.
Since $u$ has order $d-1$, we can find an eigenbasis $\{ \ket{u_i} \}_{i=0}^{d-2}$ such that the eigen-decomposition of $U$ is
	U = \sum_{i=0}^{d-2} \omega_{d-1}^i \ketbra{u_i}{u_i},
then $\Psi_1(x_3)$ and $\Psi_1(x_4)$ are  
	A_3 = B_3 =\Psi_1(x_3) = &\ketbra{u_0}{u_0} +\omega_{d-1}^{(d-1)/2}\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}}\\ + 
	&\sum_{k=1}^{(d-3)/2}\left( \omega_{d-1}^k\ketbra{u_k}{u_{d-1-k}} + \omega_{d-1}^{-k}\ketbra{x_{d-1-k}}{x_k}\right)\\ 
	A_4 = B_4  =\Psi_1(x_4) = &\ketbra{u_0}{u_0} +\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}} \\+
	 &\sum_{k=1}^{(d-3)/2}\left(\ketbra{u_{d-1-k}}{u_k} + \ketbra{u_k}{u_{d-1-k}}\right).
The conjugation relations in $C_r$ determines the representations of 
the rest of the $x_i$'s from $x_1,x_2,x_3$ and $x_4$. 
For example, if $x_5 = x_1x_2x_1 \in C_r$, then
	\Psi_1(x_5) = \Psi_1(x_1)\Psi_1(x_2) \Psi_1(x_1).

>>>>

\begin{definition}[Linear system game]
 Let $Hx = c$ be an $m \times n$ system of linear equations over $\Z_2$,
 where $H$ is an $m$-by-$n$ matrix with entries in $\Z_2 = \{0,1\}$ and 
 $c$ is a length-$n$ vector with entries in $\Z_2$. 
 The associated linear system game involves two
 players Alice and Bob, where Alice is given an equation number $i \in \calX = [m]+1$ and replies with $a \in \calA = \Z_2^{\times n}$,
 and Bob is given a variable number $j \in \calY = [n]+1$ and replies with an assignment $b \in \calB = \Z_2$. The winning condition is 
 that Alice's assignment to the variables should satisfy equation $i$ and Alice's $j$-th assignment $a(j)$ should match $b$.
 Formally, the winning condition is 
 \begin{align*}
 	a(j) &= b && \text{(Consistency)} \\
	\sum_{k= 1}^n H(i,k) a(k) &\equiv c(i) \pmod 2. &&\text{(Constraint satisfaction)},
 \end{align*}
 for all $(i,j) \in \calX \times \calY$. 
\end{definition}
The scoring function of linear system games always maps an input-output pair to $\{0,1\}$, 
so later when we say a quantum strategy wins a linear system game perfectly, we mean that 
$V(a,b,x,y) =0$ implies that $\pr{ab}{xy} = 0$.  \carl{Make this clear in the definition itself.}
We focus on quantum strategies for the linear system game presented in terms of binary observables.
\begin{definition}[Quantum strategy of a linear system game]
\label{def:q_strat}
A quantum strategy presented in terms of observables for the linear system game $(Hx = c)$ consists of 
\begin{enumerate}
	\item a pair of finite Hilbert spaces $\calH_A$ and $\calH_B$;
	\item a collection of binary observables $B_j$, $1 \leq j \leq n$, on $\calH_B$
	such that $B_j^2 = \1$ for every $1 \leq j \leq n$;
	\item a collection of binary observables $A_{ij}$, $1\leq i \leq m$, $1\leq j\leq n$ 
	on $\calH_A$ such that 
	\begin{enumerate}
		\item $A_{ij}^2 = \1$ for every $i,j$,
		\item $\Pi_j A_{ij}^{H(i,j)} = (-\1)^{c(i)}$ for every $i$, and
		\item $A_{il}A_{ik} = A_{ik}A_{il}$ for every $i$ and $H(i,l) = H(i,k) =1$;
	\end{enumerate} 
	and
	\item a quantum state $\ket{\psi} \in \calH_A \x \calH_B$.
\end{enumerate}
\end{definition}
Note that any quantum strategy presented in terms of binary observables can be 
converted to a quantum strategy presented in terms of projective measurement by looking into
the spectrum decompositions of the observables.

%It has been shown in Ref.~\cite{cleve2014} that the linear system game has a perfect strategy 
%satisfying conditions in \cref{def:q_strat} if and only if the linear system has a finite-dimensional
%operator solution in the following sense.  \carl{There's a missing reference here?}
%\begin{definition}[Operator solution of a linear system]
%\label{def:op_sol}
%	An operator solution to a linear system $Hx =c$ over $\Z_2$ is a sequence of \hf{finite-dimensional} Hermitian 
%	operators \hf{with finite entries}: $A_1, A_2, \dots A_n$ on a Hilbert space $\calH$ such that \carl{(What does the word ``bounded'' mean here?  It might
%	be best to just state the definition for finite dimensions only.)}
%	\begin{enumerate}
%		\item $A_i^2 = \1$, i.e. $A_i$ is a binary observable, for all $1 \leq i \leq n$;
%		\item If $x_l$ and $x_k$ appear in the same equation, then $A_l$ and $A_k$ commute;
%		\item for all $1 \leq i \leq m$,
%		\begin{align*}
%			\Pi_{k=1}^n A_k^{H(i,k)} = (-1)^{c(i)}\1.
%		\end{align*}
%	\end{enumerate}
%	A finite dimensional operator solution to a linear system $Hx = c$ over $\Z_2$ is an operator
%	solution in which the Hilbert space is finite-dimensional.
%\end{definition}
%Perfect quantum strategies can be extracted from operator solutions and vice versa.
Another angle to look at the linear system game ($Hx = c$) is a finitely presented group
over $\Z_2$, which is called the solution group.
\begin{definition}[Solution group of a linear system game]
	\label{def:presentation}
	Let $Hx = c$ be an $m \times n$  linear system. The solution group of this system
	is the group
	\begin{align*}
		\Gamma(H,c) := \ip{
		x_1,\dots x_n, J: &J^2 = x_i^2 = e, Jx_i = x_iJ \text{ for all }1 \leq i \leq n, \\
				& \Pi_{j=1}^n x_j^{H(i,j)} = J^{c(i)} \text{ for all } 1 \leq i \leq m, \text{ and } \\
				& x_l x_k = x_k x_l \text{ if } H(i,k) = H(i,l) = 1 \text{ for some } i
				} .
	\end{align*}
\end{definition}
Let $\Psi$ be a finite-dimensional representation of $\Gamma(H,c)$ such that $\Psi(J) = -\1$ on the vector space $\C^d$, then a prefect strategy for 
the linear system game ($Hx = c$) is given by 
\begin{enumerate}
	\item $A_{ij} = \Psi(x_j)$ for all $ 1 \leq i \leq m$ and $1 \leq j \leq n$,
	\item $B_j = \Psi(x_j)$ for all $1 \leq j \leq n$,
	\item the maximally entangled state $\ket{\psi} = \frac{1}{\sd} \sum_{k=1}^d \ket{k}\ket{k}$.
\end{enumerate}
We follow a similar approach to construct our ideal strategy. However, our strategy uses a different maximally entangled state,
so we justify our strategy more carefully.
For concepts related to group presentations, we refer to Sec.~$2$ of Ref.~\cite{slofstra2017}.
For concepts related to group representations, we refer to Sec.~$2.5$ of Ref.~\cite{coladan2017}.

@@

In Slofstra's seminal work~\cite{slofstra2017} embeds the group
\begin{align}
	K = \ip{ x,y,a,b:a^2=b^2=e, ab=ba, yay^{-1} = a, yby^{-1} = ab, xyx^{-1}=y^2}
\end{align}
into a linear system game such that the relations in the definition of $K$ can be reproduced from the
combination of the equations of the linear system game. The special relation $xyx^{-1} = y^2$ inspired 
our work.
\hf{We generalize this relation and make he solution group of $\LS_r$ the embedding of the 
following group}
\begin{align}
	\Pg_r= \langle u, o : uou^{-1} = o^r \rangle, \text{ for } r \in \N.
\end{align}
In other words, relations in the presentation of the solution group of $\LS$ can be combined to derive the
relation $uou^{-1} = o^r$.  
\begin{proposition}
	\label{prop:embed}
	The group $\Pg_r$ can be embedded into a linear system game $\LS_r$ over $\Z_2$,
	with the numbers of variables, $n_r := 17r + 73$, 
	and the number of equations, $m_r =15r + 61$, where each equation involves $3$ variables.
	\carl{You need to make this a more precise statement.  (It sounds as if you're saying 
	that the numbers of variables and equations is independent of $r$, which I'm pretty sure is not true.)}
\end{proposition}
The process of embedding $\Pg_r$ into the solution group of $\LS$ follows the recipe given in the proofs of
Proposition~$4.8$, Lemma~$4.4$ and Proposition $4.2$ of Ref.~\cite{slofstra2017}.
The order of applying the results is the reverse of the order they are presented in Ref.~\cite{slofstra2017}.
We give details of this embedding process in \cref{sec:power2} for $r = 2$, \cref{sec:power3} for $r = 3$, 
and \cref{sec:power5} for $r = 5$.

@@

Since Bob gets the same symbols $1$ and $2$ in different sub-tests, 
the observables $A_1 = B_1 = \Psi_1(x_1)$ and $A_2 = B_2 = \Psi_1(x_2)$ are extended from $B_1|_V$ and $B_2|_V$ as follows
%\begin{align}
%	B_1 = \ketbra{x_0}{x_0} + 
%	\sum_{k=1}^{(d-1)/2}\left( e^{ik\pi/2d}\ketbra{x_k}{x_{d-k}} + e^{-ik\pi/2d}\ketbra{x_{d-k}}{x_k}\right)\\
%	B_2 = \ketbra{x_0}{x_0} + 
%	\sum_{k=1}^{(d-1)/2}\left( e^{ik\pi/2d}\ketbra{x_{d-k}}{x_k} + e^{-ik\pi/2d}\ketbra{x_{k}}{x_{d-k}}\right)
%\end{align}
\begin{align}
	A_1 = B_1 = \Psi_1(x_1) &= \sum_{k=1}^{(d-1)/2}\left( \omega_d^k\ketbra{x_k}{x_{d-k}} + \omega_d^{-k}\ketbra{x_{d-k}}{x_k}\right)\\
	A_2 = B_2 = \Psi_1(x_2) &= \sum_{k=1}^{(d-1)/2}\left(\ketbra{x_{d-k}}{x_k} + \ketbra{x_k}{x_{d-k}}\right).
\end{align}
It can be checked that $X = \Psi_1(x_1x_2) = \sum_{i \in \Zd} \omega_d^i \ketbra{x_i}{x_i}$ 
The relation $uxu^{-1} = x^r$ and $X$ determine that 
\begin{align}
	U =\Psi_1(u) = \Psi_1(x_3x_4) =  \sum_{i \in \Zd} \ketbra{x_{r^{-1}i}}{x_i},
\end{align}
\hf{where $r^{-1}$ is the multiplicative inverse of $r$ in $\Zd$.
All the multiplications done on the label $i$ of the state $\ket{x_i}$ are within the group $\Zd$.}
The first step of the embedding procedure in the proof of \cref{prop:embed} requires
the commutativity between $U$ and $B_2$, so we prove the commutation relation first and
then give $\Psi_1(x_3)$ and $\Psi_1(x_4)$.
The commutation relation can be checked as follows,
\begin{align}
	UB_2U\ct = \sum_{i=1}^{d-1} U\ketbra{x_i}{x_{d-i}}U\ct = \sum_{i=1}^{d-1} \ketbra{x_{r^{-1} i}}{x_{r^{-1}(d-i)}}.
\end{align}
Let $i_1 = i r^{-1} \in \Zd$ and $i_2  = r^{-1} (d-i) \in \Zd$, then
\begin{align*}
	r(i_1 + i_2) \equiv  i + (d-i) \equiv d \pmod{d} .
\end{align*}
Let $i_1 + i_2= x \in \{2, 3 \dots 2d-2\}$, then
\begin{align}
	rx \equiv d \pmod{d}
\end{align}
Since $d$ is an odd prime number and $r < d$, then $r$ cannot divide $d$ and the only valid value of $x$ is $d$.
Hence, conjugation by $U$ will transform $\ketbra{x_i}{x_{d-i}}$ into another term of the same form.
Now suppose for some $1 \leq i < i' \leq d-1$ and $U\ketbra{x_i}{x_{d-i}}U\ct = U\ketbra{x_{i'}}{x_{d-i'}}U\ct$,
it means that in $\Zd$, $i r^{-1} = i' r^{-1}$ and $i = i'$, which contradicts the fact that $i \neq i'$.
What we have shown so far is that conjugation by $U$ only permutes the terms of $B_2$, so
\begin{align}
	UB_2U\ct = B_2.
\end{align}

The decomposition of $U$ into $\Psi_1(x_3)$ and $\Psi_1(x_4)$ is similar to the decomposition of $X$.
Since $u$ has order $d-1$, we can find an eigenbasis $\{ \ket{u_i} \}_{i=0}^{d-2}$ such that the eigen-decomposition of $U$ is
\begin{align}
	U = \sum_{i=0}^{d-2} \omega_{d-1}^i \ketbra{u_i}{u_i},
\end{align} 
then $\Psi_1(x_3)$ and $\Psi_1(x_4)$ are  
\begin{align*}
	A_3 = B_3 =\Psi_1(x_3) = &\ketbra{u_0}{u_0} +\omega_{d-1}^{(d-1)/2}\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}}\\ + 
	&\sum_{k=1}^{(d-3)/2}\left( \omega_{d-1}^k\ketbra{u_k}{u_{d-1-k}} + \omega_{d-1}^{-k}\ketbra{x_{d-1-k}}{x_k}\right)\\ 
	A_4 = B_4  =\Psi_1(x_4) = &\ketbra{u_0}{u_0} +\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}} \\+
	 &\sum_{k=1}^{(d-3)/2}\left(\ketbra{u_{d-1-k}}{u_k} + \ketbra{u_k}{u_{d-1-k}}\right).
\end{align*}
Next we will show that 
\begin{align}
	A_3\x B_3 \ket{\psi} = \ket{\psi} && A_4 \x B_4 \ket{\psi} = \ket{\psi}.
\end{align}
For this purpose, we use a different expression of $\ket{\psi}$, which is
\begin{align}
	\ket{\psi} = \frac{1}{\sqrt{d}} \sum_{j=0}^{d-2} \ket{r^j} \ket{r^{d-1-j}}.
\end{align}
Then the eigenvectors of $U$ are 
\begin{align}
	\ket{u_k} = \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \omega_{d-1}^{jk} \ket{r^j}.
\end{align}
Hence we can express $\ket{r^j}$ in terms of $\ket{u_k}$ as 
\begin{align}
	\ket{r^j} = \frac{1}{\sqrt{d-1}} \sum_{k=0}^{d-2} \omega_{d-1}^{-jk} \ket{u_k}.
\end{align}
Then $B_4$ acts on $\ket{r^j}$ as 
\begin{align}
	B_4 \ket{r^j} =& \frac{1}{\sqrt{d-1}} B_4\left(\ket{u_0} + \omega_{d-1}^{-j(d-1)/2}\ket{u_{(d-1)/2}}  + 
	\sum_{k=1}^{(d-3)/2} (\omega_{d-1}^{-jk} \ket{u_k} + \omega_{d-1}^{jk} \ket{u_{d-1-k}})\right) \\
	=&\frac{1}{\sqrt{d-1}} \left(\ket{u_0} + (-1)^j\ket{u_{(d-1)/2}}  + 
	\sum_{k=1}^{(d-3)/2} (\omega_{d-1}^{-jk} \ket{u_{d-1-k}} + \omega_{d-1}^{jk} \ket{u_{k}})\right) \\
	=& \ket{r^{d-1-j}}.
\end{align}
We first verify that $U \x U \ket{\psi} = \ket{\psi}$
\begin{align}
	U \x U \ket{\psi} &= \frac{1}{\sqrt{d-1}}\sum_{j = 0}^{d-2} \ketbra{ r^{j}r^{-1}}{r^j} \ket{r^j} \x \ketbra{r^{d-1-j} r^{-1}}{r^{d-1-j}} \ket{r^{d-1-j}} \\
	&=\frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \ket{r^{j-1}}\ket{r^{d-1-j}} = \ket{\psi},
\end{align}
where we use the fact that $\ket{r^{-1}} = \ket{r^{d-2}}$.
Then we show that $A_4 \x B_4 \ket{\psi} = \ket{\psi}$ as 
\begin{align}
	A_4 \x B_4 \ket{\psi} = \frac{1}{\sqrt{d-1}}  \sum_{j=0}^{d-2} A_4 \x B_4 \ket{r^j} \ket{r^{d-1-j}} 
	= \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \ket{r^{d-1-j}} \ket{r^{j}} =\ket{\psi},
\end{align}
which combined with the previous fact implies that $A_3 \x B_3 \ket{\psi} = \ket{\psi}$.

The conjugation relations in $C_r$ determines the representations of 
the rest of the $x_i$'s from $x_1,x_2,x_3$ and $x_4$. 
For example, if $x_5 = x_1x_2x_1 \in C_r$, then
\begin{align}
	\Psi_1(x_5) = \Psi_1(x_1)\Psi_1(x_2) \Psi_1(x_1).
\end{align}
